---
title: "p8105_hw5_qz2266"
author: "Qing Zhou"
date: "2022-11-09"
output: github_document
---


```{r packages}
library(tidyverse)
```


### Problem 2
```{r read_data}
homicide_df = read.csv("data/homicide-data.csv") 
```

```{r tidy}
# change date format
homicide = transform(homicide_df, reported_date = as.Date(as.character(reported_date), "%Y%m%d")) %>%   
  
# create a city_state variable
  mutate(city_state = str_c(city, state, sep = ", "))     
```

This dataset contains information about `r nrow(homicide)` homicides in `r nrow(homicide %>% distinct(city_state))` U.S. cities in `r nrow(homicide %>% distinct(state))` states reported from 2007 to 2017. In each homicide, the victim's name, rage, age, and sex are reported, as well as the disposition for each case.

Note: There are two cities with the name of Tulsa. However, "Tulsa, AL" has only one data included. It's possible a mistake in data entry. Moreover, I checked online but couldn't find a city called Tulsa in Alabama. If it's a typo, then there are only 50 cities in this dataset.


#### Summary of the total number of homicides and the number of unsolved homicides within cities
```{r classify}
homicide_sum = 
homicide %>%
mutate(
    solution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
 select(city_state, solution) %>% 
  
 # filter out the city of Tulsa_AL
 filter(city_state != "Tulsa, AL") 

homicide_sum
```

```{r summerize}
disposition_city = 
  homicide_sum %>% 
  group_by(city_state) %>% 
  summarize(
    homi_total = n(),
    homi_unsolved = sum(solution == "unsolved"))

disposition_city
```


#### Prop.test for Baltimore, MD
```{r}
baltimore_prop = prop.test(
  disposition_city %>% filter(city_state == "Baltimore, MD") %>% pull(homi_unsolved), 
  disposition_city %>% filter(city_state == "Baltimore, MD") %>% pull(homi_total)) %>% 
  broom::tidy()
```

```{r}
# pull the estimated proportion and confidence intervals from the tidy dataframe.
tibble(estimate = baltimore_prop %>% pull(estimate),
       conf.low = baltimore_prop %>% pull(conf.low),
       conf.high = baltimore_prop %>% pull(conf.high))
```


#### Prop.test for all cities
```{r}
city_prop = 
  disposition_city %>% 
  mutate(
    prop_result = map2(.x = homi_unsolved, .y = homi_total, ~prop.test(x = .x, n = .y)),
    tidy_result = map(.x = prop_result, ~broom::tidy(.x))
  ) %>% 
  select(-prop_result) %>% 
  unnest(tidy_result) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


#### Create a plot that shows the estimates and CIs for each city
```{r}
city_prop %>% 
  mutate(city_state = factor(city_state)) %>% 
  mutate(city_state = forcats::fct_reorder(city_state, estimate)) %>% 
  
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point(color = "red") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +

  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = rel(0.8))) +
  labs( x = "City_State",
    y = "Estimated proportion of unsolved cases",
    title = "Proportion of Unsolved Homicides in the U.S.")
```

The Plot shows that Chicago, IL was the city with the highest proportion of unsolved homicide vs. total homicide. There was a nearly 75% homicide cases unsettled. On the other hand, Richmond has the lowest proportion among the 50 cities. There was only around 25% cases unsettled.


### Problem 3

#### Set the function and ttest
```{r funtion}
set.seed(1)

sim_nor = function(n = 30, mu = 0, sigma = 5){
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma))
  ttest = t.test(x = sim_data, conf.level = 0.95) %>%
    broom::tidy() %>%
    select(estimate, p.value)
}
```


#### Set μ=0. Generate 5000 datasets from the model
```{r}
sim_mu_0 = rerun(5000, sim_nor(mu = 0)) %>%
  bind_rows()

head(sim_mu_0)
```


#### Repeat the above for μ={0,1,2,3,4,5,6}
```{r}
sim_result =
  tibble(mu = c(0,1,2,3,4,5,6)) %>%
  mutate(output = map(.x = mu, ~rerun(5000, sim_nor(mu = .x))),
         result = map(output, bind_rows)) %>%
  unnest(result) %>% 
  select(-output)


```

#### Make a plot showing the proportion of times the null was rejected

```{r}
power_plot =
  sim_result %>%
  group_by(mu) %>%
  mutate(
    total = n(),
    rej_null = sum(p.value < 0.05),
    power = rej_null/total,
    mu = as.factor(mu)
  ) %>%
  
  ggplot(aes(x = mu, y = power, color = mu)) +
  geom_point(size = 3) +
  
  theme_bw() +
  labs(
    title = "The Power of the Tests",
    x = "μ",
    y = "power"
  )

power_plot

```

#### Make a plot showing the average estimate of μ^ and the true value of μ

```{r}
total_plot =
  sim_result %>%
  group_by(mu) %>%
  summarize(avg_estimate = mean(estimate)) %>%
  mutate(mu = as.factor(mu)) %>%
  
  ggplot(aes(x = mu, y = avg_estimate, color = mu)) + 
  geom_point(size = 3) +
  
  labs(
    x = "True μ", 
    y = "Average of Estimated μ_hat", 
    title = " Average of Estimated  vs. True Mean Among All Samples"
  )

total_plot
```


#### Make a plot of the average estimate of μ^ only in samples for which the null was rejected and the true value of μ on the x axis

```{r}

```

